\documentclass[11pt]{extreport}
\usepackage[fontsize=10.5pt]{scrextend}
\usepackage{latexsym}
\usepackage[default]{lato}
\usepackage{fontawesome5}
\usepackage[empty]{fullpage}
\usepackage{fontawesome, graphicx}
\usepackage{titlesec}
\usepackage{marvosym}
\newcommand*{\phoneReceiverB}{{\fontspec{quivira.otf}\symbol{"1F4DE}}}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{MidnightBlue}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\  
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \textcolor{MidnightBlue}{Yazan Haddad}} \\ \vspace{8pt}
    \small \raisebox{-0.25ex}{\faPhone} \underline{437-450-0117} $|$ {\faEnvelope \, \underline{haddad.yazan117@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/hxddad}{\faLinkedin \, \underline{hxddad}} $|$ \href{https://github.com/hxddad}{\faGithub \, \underline{hxddad}}
\end{center}

%-----------EDUCATION-----------
\section{\textcolor{MidnightBlue}{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {York University}{Toronto, ON}
      {Bachelor of Engineering in Software Engineering}{Expected: Apr. 2026} 
      \vspace{10pt}\\
      \textbf{Coursework:} Object-Oriented Programming, Data Structures, Embedded Systems, Digital Logic Design.\\
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\textcolor{MidnightBlue}{Experience}}
    \resumeSubHeadingListStart
    \resumeSubheading
        {Lassonde Engineering Society}{Remote}
        {Web Developer}{May 2024 - Present}
        \resumeItemListStart
            \resumeItem{Developed and launched a website using \textbf{React} \& \textbf{Tailwind CSS}, enhancing academic resources for \textbf{720+} EECS Engineering students at York University.}
            \resumeItem{Created and curated detailed guides and resources for \textbf{30+} courses, including FAQs and additional support materials, resulting in improved student performance and satisfaction.}
            \resumeItem{Incorporated club executive feedback and provided regular progress updates within strict timelines, enhancing user satisfaction and alignment with stakeholder expectations.}
        \resumeItemListEnd
    \resumeSubheading
        {Student Support Application Development Council}{Remote}
        {Application Developer}{Jan. 2024 - Apr. 2024}
        \resumeItemListStart
            \resumeItem{Contributed to helpful open-source tools for York University students, including a \textbf{dining app} with a \textbf{team of 5}, featuring \textbf{85+} restaurants across York University.}
            \resumeItem{Utilized \textbf{BeautifulSoup \& Python} to parse and filter data from York University's dining directory, enhancing user search with \textbf{filters} for dietary restrictions, cultural cuisine, and locations, improving search efficiency by \textbf{25\%}.}
            \resumeItem{Improved code quality and robustness using \textbf{Java}, conducting unit tests with \textbf{JUnit}, covering over \textbf{95\%} of the codebase and addressing edge cases.}
        \resumeItemListEnd
    \resumeSubheading
        {Computing Students Hub}{Toronto, ON}
        {Club Executive}{Sept. 2024 - Present}
        \resumeItemListStart
        \resumeItem{Drove member engagement in a club of  \textbf{1700+} students by assisting in organizing events, workshops and meetups.}
        \resumeItem{Led outreach efforts with \textbf{15+} club executives, volunteers and boosting community participation by \textbf{12\%}.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\textcolor{MidnightBlue}{Projects}}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\underline{ArduinoVid-19 Assessment}} $|$ \emph{Java, Arduino Uno}}{}
        \resumeItemListStart
            \resumeItem{Implemented a COVID-19 screening assessment using \textbf{Java \& Arduino Uno} with a temperature sensor.}
            \resumeItem{Measured and plotted \textbf{temperature-zone graphs} using sensor data, with a mean accuracy of \textbf{33.1°C (sensor)} compared to \textbf{36.2°C (thermometer)}, alerting users to possible fever conditions.}
            \resumeItem{Integrated libraries \textbf{JSSC \& Firmata4j} to communicate with board pins, processing over \textbf{10 sensor readings} per trial with an average temperature bias of \textbf{3.1°C} between thermometer and sensor.}
            \resumeItem{Designed and implemented \textbf{Java Swing dialogue boxes} for user interactions, improving user input accuracy by providing \textbf{real-time alerts} based on sensor readings.}
        \resumeItemListEnd
           \resumeProjectHeading
            {\textbf{\underline{Soccer Analytics Tracker}} $|$ \emph{Python, OpenCV, YOLO}}{}
        \resumeItemListStart
           \resumeItem{Applied \textbf{KMeans} clustering and \textbf{OpenCV} for player segmentation, identifying jersey colours achieving \textbf{98\%} accuracy.}
            \resumeItem{Fine-tuned \& designed \textbf{YOLOv8} models using \textbf{Ultralytics} for object detection, improving accuracy with custom datasets.}
            \resumeItem{Utilized \textbf{optical flow }algorithms to track camera movement and measured player speed and distance in video footage.}
            \resumeItemListEnd
            \resumeProjectHeading
            {\textbf{\underline{AniDex}} $|$ \emph{React.js, Node.js, Express.js, MongoDB}}{}
        \resumeItemListStart
            \resumeItem{Built a full-stack application using the \textbf{MERN stack} \& \textbf{Jikan API}, enabling users to search \& add anime to watch list.}
            \resumeItem{Optimized API call efficiency, reducing load times by \textbf{30\%} improving user retention.}
            \resumeItem{Allowed users to perform \textbf{CRUD} operations on watch list using \textbf{Node.js, Express.js and MongoDB}}
            \resumeItem{Designed responsive UI with \textbf{React} and \textbf{Material-UI}, enhancing user experience by  \textbf{15\%}.}
        \resumeItemListEnd
        \resumeItemListEnd
        
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{\textcolor{MidnightBlue}{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Java, Python, HTML, CSS, JavaScript, SQL.} \\
     \textbf{Frameworks \& Developer Tools}{: Node.js, Express.js, React,js, Git, Unix/Linux, JUnit, Flask, MongoDB.} \\
     \textbf{Libraries}{: JSSC, Firmata4j, Princeton StdLib, BeautifulSoup.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
